---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/AzureDatalakeStore)](https://cran.r-project.org/package=AzureDatalakeStore)
[![Travis-CI Build Status](https://travis-ci.org/ijlyttle/AzureDatalakeStore.svg?branch=master)](https://travis-ci.org/ijlyttle/AzureDatalakeStore)
[![Coverage Status](https://img.shields.io/codecov/c/github/ijlyttle/AzureDatalakeStore/master.svg)](https://codecov.io/github/ijlyttle/AzureDatalakeStore?branch=master)

# AzureDatalakeStore

## Overview

This package is used to access the datalake store itself.


## What we will need


## Installation

__AzureDatalakeStore__ is not yet available on CRAN. You may install from GitHub:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ijlyttle/AzureDatalakeStore")
```

If you encounter a clear bug, please file a minimal reproducible example on [github](https://github.com/ijlyttle/AzureDatalakeStore/issues). 

## Code of conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
